Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2018-06-11 hpmoon-asoco.tex
Some typos fixed

\begin{bluecolor}
One of the  methods most extensively used to deal with high-dimensional multi-objective optimization problems are distributed co-evolutionary algorithms. %Pablo: reducing previous two paragraphs into one 
However, only
decomposable problems could strictly be implemented in parallel this
way. 
A new parallel island-model evolutionary algorithm approach, which we call {\em selective operator application}, is used here to deal with un-decomposable
problems: % so we are saying that high-dimensional multi-objective
          % problems are a challenge, but we are presenting a solution
          % for non-decomposable problems. What's what? - JJ
% Still not addressed - JJ PABLO: rewritten almost all the abstract.
instead of sharing parts
of individuals, each island, hosted by a single processor, applies the variation operators to a
specific subset of the whole individual. This avoids extra steps to recompose the complete individuals from other islands before evaluation. 
% 
 In this paper, we intend to prove that automatically setting the size of these
 overlapping section, since it focuses the search between borders of the different search spaces, is able to obtain better
 results than using the same size independently of the number of islands. In order to prove that, we
 have compared it to other parallel evolutionary
techniques considering different number of islands, chromosome sizes
and benchmarks. The analysis of the obtained experimental results, by
using different metrics, shows that our approach can provide
statistically significant improvements with respect to the base
algorithm in high-dimensional, un-decomposable, multi-objective problems. 
%
Results also show that the relation between the number of
islands (subpopulations) and the length of the chromosome (number of
decision variables) is also a relevant factor to determine the most
efficient alternative to distribute the decision variables: the higher
the dimensionality and the overlapping, the greater the benefit of distribution in a
large number of islands.
This opens up a new challenge to be addressed in the future, by
experimenting on new ways to calculate the overlapping sizes depending
of different factors and parameters.
\end{bluecolor}

>>>>

\begin{bluecolor}
One of the  most extensively used methods to deal with high-dimensional, multi-objective optimization problems are distributed co-evolutionary algorithms. 
However, only
decomposable problems could strictly be implemented in parallel this
way. 
A new parallel island-model evolutionary algorithm approach, which we call {\em selective operator application}, is used here to deal with un-decomposable
problems: 
instead of sharing parts
of individuals, each island, hosted by a single processor, applies the variation operators to a
specific subset of the whole individual. This avoids extra steps to recompose the complete individuals from other islands before evaluation.

 In this paper, we intend to prove that automatically setting the size of these
 overlapping sections, since it focuses the search between borders of the different search spaces, is able to obtain better
 results than using the same size independently of the number of islands. In order to prove that, we
 have compared this method to other parallel evolutionary
techniques considering different number of islands, chromosome sizes
and benchmarks. The analysis of the obtained experimental results, by
using different metrics, shows that our approach can provide
statistically significant improvements with respect to the base
algorithm in high-dimensional, un-decomposable, multi-objective problems.

Results also show that the relation between the number of
islands (subpopulations) and the length of the chromosome (number of
decision variables) is also a relevant factor to determine the most
efficient alternative to distribute the decision variables: the higher
the dimensionality and the overlapping, the greater the benefit of distribution in a
large number of islands.
This opens up a new challenge to be addressed in the future, by
experimenting with new ways to calculate the overlapping sizes depending
of different factors and parameters.
\end{bluecolor}
